Simplified-spatial-availability-example

### 2023-05-18 Draft-manuscript-tobemoved.Rmd
Added 'multi-mode-acc-methods', a manuscript for multi-model accessibility draft.

```{r load-packages, include=FALSE, cache=FALSE}
library(tidyverse)
library(sf)
library(fitdistrplus)
library(ggplot2)
library(readxl) #imports excel files
library(patchwork)
library(cowplot)
```

@@

- lit has found that emissions reduciton should not result in inequalities..

>>>>

```{r load-packages, include=FALSE, cache=FALSE}
library(tidyverse)
library(sf)
library(fitdistrplus)
library(ggplot2)
library(readxl) #imports excel files
library(patchwork)
library(cowplot)
library(ggspatial)
```

@@

- lit has found that emissions reduction should not result in inequalities..

### 2023-05-18 Simplified-spatial-availability-example.Rmd
Added 'multi-mode-acc-methods', a manuscript for multi-model accessibility draft.

Calculate spatial availabilty:
```{r}
OD_SA <- OD_2 %>%
  mutate(catch = 1) %>%
  mutate(SA_ij = sp_avail(., 
                          o_id = VORI_CD_ZT208,
                          d_id = VDES_CD_ZT208,
                          pop = workers,
                          opp = jobs,
                          r = catch,
                          f = f))
```

@@

<!-- AS finished here May 31, am stuck on how to shift car trips to transit (in a way that's flexible and will allow us to easily toggle the modal shift scenarios (i.e., instead of 100% transit, maybe 80%/10/10 transit/bike/walk)) -->

>>>>

Calculate spatial availability:
```{r}
OD_SA <- OD_2 %>%
  mutate(catch = 1) %>%
  mutate(SA_ij = sp_avail(., 
                          o_id = VORI_CD_ZT208,
                          d_id = VDES_CD_ZT208,
                          pop = workers,
                          opp = jobs,
                          r = catch,
                          f = f))
```

@@

<!-- AS finished here May 31, am stuck on how to shift car trips to transit (in a way that's flexible and will allow us to easily toggle the modal shift scenarios (i.e., instead of 100% transit, maybe 80%/10/10 transit/bike/walk))

- 1) add akk trips (for all modes) to the dataset as 0
- 2) allocation factors for trips going INTO madrid LEZ, a factor of 1 (car trip) proportional to other modes by distance-->
